The imprint of global magma oceans on exoplanet demographics

### 2023-03-09 src/tex/ms.tex
move description of priors

@@

\subsection{Bayesian model comparison}
We are now ready to assess the relative plausibility of $H_{\mathrm{rgh}}$ and $H_0$ given the synthetic data we have generated, assigning equal a~priori~ probabilities to these models.
This is done by comparing the Bayesian evidence $\mathcal{Z}$ of the models, which we estimate with the nested sampling~\citep{Skilling2004} algorithm \emph{dynesty}~\citep{Speagle2020}.
Our criterion to reject the null hypothesis is
\begin{equation}
\Delta \ln \mathcal{Z}  = \ln \mathcal{Z}_\mathrm{rgh} - \ln \mathcal{Z}_0  > 3.
\end{equation}
%The chosen threshold roughly corresponds to the $p = 0.05$ threshold for statistical significance popular in frequentist approaches.\todo{CITATION}

A sensible choice of priors is central for evidence estimation via nested sampling.
As the parameters we are interested in recovering, $S_\mathrm{thresh}$ and $x_{H_2O}$, are poorly constrained by previous data, we used relatively uninformative priors to sample the entire physically plausible parameter space.
For $S_\mathrm{thresh}$, we chose a uniform prior in $[\prSmin,\prSmax]\, \SI{}{\watt\per\meter\squared}$.
We sample $x_{H_2O}$ from a log-uniform distribution to imply scale-invariant ignorance.
Its boundaries $[\prWRRmin, \prWRRmax]$ are motivated by the water mass fractions covered by the geophysical models~(Sect.~\ref{sec:met_rghmodel}).
Finally, we adopt a broad, uniform prior for $\langle R_\mathrm{P}\rangle_\mathrm{out}$ bound by $[\prRmin, \prRmax] \, \mathrm{R_\oplus}$.
We then ran the nested sampler to compute the evidence and sample the posterior distributions.

>>>>

A sensible choice of priors is central for evidence estimation via nested sampling.
As the parameters of interest are poorly constrained by previous data, we used relatively uninformative priors to sample the entire physically plausible parameter space.
For $S_\mathrm{thresh}$, we chose a uniform prior in $[\prSmin,\prSmax]\, \SI{}{\watt\per\meter\squared}$.
We sample $x_{H_2O}$ from a log-uniform distribution to imply scale-invariant ignorance.
Its boundaries $[\prWRRmin, \prWRRmax]$ are motivated by the water mass fractions covered by the geophysical models~(Sect.~\ref{sec:met_rghmodel}).
For $f_\mathrm{rgh}$, we chose a uniform prior in $[0, 1]$.
Finally, we adopt a broad, uniform prior for $\langle R_\mathrm{P}\rangle_\mathrm{out}$ bound by $[\prRmin, \prRmax] \, \mathrm{R_\oplus}$.

@@

\subsection{Bayesian model comparison}
We are now ready to assess the relative plausibility of $H_{\mathrm{rgh}}$ and $H_0$ given the synthetic data we have generated, assigning equal a~priori~ probabilities to these models.
This is done by comparing the Bayesian evidence $\mathcal{Z}$ of the models, which we estimated with the nested sampling~\citep{Skilling2004} algorithm \emph{dynesty}~\citep{Speagle2020}.
We initialized the sampler with the priors defined above to let it estimate the evidence and sample the posterior distributions.
Our criterion to reject the null hypothesis is
\begin{equation}
\Delta \ln \mathcal{Z}  = \ln \mathcal{Z}_\mathrm{rgh} - \ln \mathcal{Z}_0  > 3.
\end{equation}
%The chosen threshold roughly corresponds to the $p = 0.05$ threshold for statistical significance popular in frequentist approaches.\todo{CITATION}
